%-------------------------
% Resume in LaTeX
% Author: Jake Gutierrez
% Based on: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT SETTINGS----------
% Sans-serif fonts
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% Serif fonts
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all headers and footers
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF readability and accessibility
\pdfgentounicode=1

%-------------------------
% Custom Commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADER----------
\begin{center}
    \textbf{\Huge \scshape Oralbayev Maksat} \\ \vspace{1pt}
    \small +7707-393-580 $|$ \href{mailto:code.datum@gmail.com}{\underline{code.datum@gmail.com}} $|$
    \href{https://www.linkedin.com/in/maxoralbay/}{\underline{linkedin.com/in/maxoralbay}} $|$
    \href{https://github.com/maxoralbay}{\underline{github.com/maxoralbay}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Regional Social-Innovative University}{Shymkent, Kazakhstan}
      {Bachelor's Degree, Physics Teacher}{2014-2016}
    \resumeSubheading
      {Engineering and Pedagogical University of Friendship of Peoples}{Shymkent, Kazakhstan}
      {Bachelor's Degree, Radio Engineering, Electronics, and Telecommunications}{2007-2011}
  \resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
   \resumeSubheading
      {Full-stack Developer}{August 2023 -- Present}
      {openTrade}{UK, London. Remote}
      \resumeItemListStart
        \resumeItem{Developed a trading bot for automating trades using CCXT and pandas-ta.}
        \resumeItem{Implemented data processing via WebSocket API for real-time market information.}
        \resumeItem{Created a crypto tracker for portfolio monitoring and market data analysis.}
        \resumeItem{Worked with smart contracts and blockchain integration using Web3.py.}
        \resumeItem{Developed and optimized technical analysis-based strategies in Pinescript for TradingView.}
      \resumeItemListEnd

      \resumeSubheading
      {Full-stack Developer}{September 2023 -- November 2024}
      {LLC Isker Group}{Part-time | Remote}
      \resumeItemListStart
        \resumeItem{Developed complex Telegram bots using Python and Telegram API.}
        \resumeItem{Optimized PostgreSQL database, wrote complex SQL queries using SQLAlchemy.}
        \resumeItem{Participated in REST API development using Django REST Framework (DRF), reducing new module development time by 25\%.}
        \resumeItem{Configured queue processing via RabbitMQ.}
        \resumeItem{Designed ETL processes for data extraction, transformation, and loading.}
        \resumeItem{Performed data parsing and logging, ensuring accuracy and completeness in analytical systems.}
      \resumeItemListEnd

    \resumeSubheading
      {Web Developer}{August 2020 -- June 2023}
      {Devex Service}{Saint Petersburg, Russia}
      \resumeItemListStart
        \resumeItem{Full-Stack Backend Development: Maintained and enhanced websites using JavaScript, Python, PHP, and developed microservices using Tarantool and Lua, reducing operational costs by optimizing database and cache systems.}
        \resumeItem{Microservice and Containerization: Built and managed microservices in Docker for company sites and apps, using Laravel, WordPress API, Django, and No-Code platforms.}
        \resumeItem{Optimization of Front end development: Led frontend development with NextJS and Vuex, improving interface performance and user engagement.}
      \resumeItemListEnd

    \resumeSubheading
      {Full-stack Developer}{July 2019 -- March 2020}
      {Perfect Systems LLC}{Moscow, Russia}
      \resumeItemListStart
        \resumeItem{Led a team developing a parsing system for collecting and analyzing reviews of doctors and medical institutions in the USA.}
        \resumeItem{Used the Web Scrapy library for automated data collection from various websites.}
        \resumeItem{Implemented bypass of site protection using proxy rotation.}
        \resumeItem{Organized delivery of collected data to Django via queues, ensuring efficient processing and storage.}
      \resumeItemListEnd

      \resumeSubheading
      {Full-stack Developer}{June 2017 -- May 2019}
      {Evrika LLC}{Shymkent, Kazakhstan}
      \resumeItemListStart
        \resumeItem{Interacted with clients and analyzed requirements: Regularly engaged with clients to understand their goals and ensure alignment of web resources with their needs.}
        \resumeItem{Programming and development: Wrote and implemented programs necessary for website functionality and support, handling both frontend and backend tasks.}
        \resumeItem{Website maintenance and troubleshooting: Managed and maintained websites, ensuring optimal performance and resolving arising issues.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SOFT SKILLS-----------
\section{Soft Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    {Project Management, Time Management, Communication, Adaptability, Problem-Solving, Teamwork, Creativity}
 \end{itemize}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Programming Languages}{: Python (versions 3.x), PHP, SQL, Lua, PineScript, JavaScript, HTML/CSS, Bash} \\
        \textbf{Frameworks}{: Django, Flask, FastAPI, Django REST Framework (DRF), Laravel, Nuxt.js, Vue, React, and others} \\
        \textbf{Databases}{: PostgreSQL, MySQL, Redis, MongoDB} \\
        \textbf{DevOps}{: Docker, Kubernetes, Jenkins, GitHub, GitLab CI/CD, GCP, VS Code, SourceTree, and more} \\
        \textbf{Libraries}{: Pandas, NumPy, SQLAlchemy, Pytest, CCXT, pandas-ta, Web3.py, Celery, Redis, aiohttp, asynchronous libraries, and more} \\
        \textbf{ETL Processes}{: Creation and maintenance for data processing} \\
        \textbf{Algorithmic Trading}{: Development of trading strategies and bots (PineScript, Alpaca API, WebSocket API)} \\
        \textbf{Web3 and NFT}{: Working with smart contracts, crypto trackers, blockchain integration} \\
        \textbf{Logging, Data Processing, and Parsing}{: Optimization of processes for analytical tasks} \\
        \textbf{Soft Skills}{: Teamwork, code review, task decomposition}
    }}
\end{itemize}
%-------------------------------------------
%-----------HOBBIES-----------
\section{Hobbies}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        Interest in advanced mathematics and financial mathematics.
    }}
\end{itemize}

\end{document}
-------------------------------------------
